%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Work Package Description  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{workpackage}{Real Life Application}
  \label{wp:app} %change and use appropriate description


  %%%%%%%%%%%%%%%%%% TOP TABLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  % Data for the top table
  \wpstart{20} %Starting Week
  \wpend{30} %End Week
  \wptype{Activity type} %RTD, DEM, MGT, or OTHER

  % Person Weeks per participant (required, max 7, * for leader)  
  % syntax: \personweeks{Participant number}{value}    (not wp leader)
  %     or  \personweeks{Participant short name}{value} (not wp leader)
  %         \personweeks*{Participant number}{value}    (wp leader)
  % for example:
  \personweeks*{georgio}{10}
  % etc.

  \makewptable % Work package summary table
    
  % Work Package Objectives
  \begin{wpobjectives}
    This work package has the following objectives:
    \begin{enumerate}
    \item Implement cogniLink to work on a controller of a wheelchair, this task derives from cogniLink as a forked project;
    \item Initiate research about Locked-in syndrome: Find suitiable use-cases and patients.
    \end{enumerate}
  \end{wpobjectives}

  % Work Package Description
  \begin{wpdescription}
    % Divide work package into multiple tasks.
    % Use \wptask command
    % syntax: \wptask{leader}{contributors}{start-m}{end-m}{title}{description}   
 
    \wptask{georgio}{georgio}{20}{22}{Task1}{
      \label{task:wp6task1}
      First Fork of cogniLink.
      A wheelchair controller/helper that can be fed command data as a replacement to the virtual HID will be designed and implemented.
    }
    \wptask{georgio}{georgio}{20}{30}{Task2}{
      \label{task:wp6task2}
      Initiation of formal research about Locked-in syndrome, patients, and practical use-case scenarios.
    }  
  \end{wpdescription}
  
  % Work Package Deliverable
  \begin{wpdeliverables}
    % Data for the deliverables and milestones  tables
    % syntax: \deliverable[delivery date]{nature}{dissemination
    % level}{description} 
    %
    % nature: R = Report, P = Prototype, D = Demonstrator, O = Other
    % dissemination level: PU = Public, PP = Restricted to other
    % programme participants (including the Commission Services), RE =
    % Restricted to a group specified by the consortium (including the
    % Commission Services), CO = Confidential, only for members of the
    % consortium (including the Commission Services).
    % 
    % \wpdeliverable[date]{R}{PU}{A report on \ldots}

    \wpdeliverable[22]{georgio}{R}{PU}{Report about integration with wheelchair.}\label{dev:wp6f1report}
    
    \wpdeliverable[30]{georgio}{P}{PU}{Forking cogniLink and merging changes needed for wheelchair integration.}\label{dev:wp6fork}

    \wpdeliverable[30]{georgio}{R}{PU}{Report about research findings and future steps towards integrating with a locked in patient. }\label{dev:wp6r2research}

    \wpdeliverable[30]{georgio}{R}{PU}{Main Main Report update with full progress accomplished after the end of WP6.}\label{dev:MR0.6}
  
  \end{wpdeliverables}
\end{workpackage}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal-main"
%%% End:
