%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Work Package Description  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{workpackage}{Model 1 n Commands}
  \label{wp:m1cN} %change and use appropriate description
  %%%%%%%%%%%%%%%%%% TOP TABLE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  % Data for the top table
  \wpstart{6} %Starting Week
  \wpend{12} %End Week
  \wptype{Activity type} %RTD, DEM, MGT, or OTHER

  % Person Weeks per participant (required, max 7, * for leader)  
  % syntax: \personweeks{Participant number}{value}    (not wp leader)
  %     or  \personweeks{Participant short name}{value} (not wp leader)
  %         \personweeks*{Participant number}{value}    (wp leader)
  % for example:
  \personweeks*{georgio}{6}
  % etc.

  \makewptable % Work package summary table
    
  % Work Package Objectives
  \begin{wpobjectives}
    This work package has the following objectives:
    \begin{enumerate*}
    \item Link the output from the Model to the virtual HID created in WP1;
    \item Map trigger thoughts to button presses; 
    \item Play a game of 1P Super Mario Bros.
    \end{enumerate*}
  \end{wpobjectives}
  
  % Work Package Description
  \begin{wpdescription}
    % Divide work package into multiple tasks.
    % Use \wptask command
    % syntax: \wptask{leader}{contributors}{start-m}{end-m}{title}{description}   

    \wptask{georgio}{georgio}{6}{12}{Task1}{
      \label{task:wp3HIDfinilazation}
      Code for linking model to virtual HID will be rechecked and finalized.
    }
    \wptask{georgio}{georgio}{6}{12}{Task2}{
      \label{task:wp3training}
      Model 1 will be trained for command B, and other commands simultaneously.
    }    
    \wptask{georgio}{georgio}{12}{12}{Task3}{
      \label{task:wp3demo}
      A game of 1P Super Mario Bros will be played.
    }    
    
    %%~\ref{task:wp3integrate}.
   
  \end{wpdescription}
  
  % Work Package Deliverable
  \begin{wpdeliverables}
    % Data for the deliverables and milestones  tables
    % syntax: \deliverable[delivery date]{nature}{dissemination
    % level}{description} 
    %
    % nature: R = Report, P = Prototype, D = Demonstrator, O = Other
    % dissemination level: PU = Public, PP = Restricted to other
    % programme participants (including the Commission Services), RE =
    % Restricted to a group specified by the consortium (including the
    % Commission Services), CO = Confidential, only for members of the
    % consortium (including the Commission Services).
    % 
    % \wpdeliverable[date]{R}{PU}{A report on \ldots}

    \wpdeliverable[8]{georgio}{D}{PU}{A demonstration of the execution of alternating commands, after successful training of the second command to model 1.}\label{dev:wp3d1}
    \wpdeliverable[11]{georgio}{R}{PU}{Report 1 on findings made while training new commands.}\label{dev:wp3r1}
    \wpdeliverable[12]{georgio}{R}{PU}{Report 2 will comapre the variation of latency between the model and the virtual HID for each code patch.}\label{dev:wp3r2}
    \wpdeliverable[12]{georgio}{P}{PU}{Code for virtual HID and updated Model 1 with multiple command recognition will be pushed to master.}\label{dev:wp3r1}
    \wpdeliverable[12]{georgio}{D}{PU}{A demonstration of the ability to play a game of 1P Super Mario Bros using cogniLink.}\label{dev:wp3prototype}
    \wpdeliverable[12]{georgio}{R}{PU}{Main Report update with full progress accomplished after the end of WP3.}\label{dev:MR0.2}
  \end{wpdeliverables}

\end{workpackage}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proposal-main"
%%% End:
